Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-07-02 paper/ifo-futureWork.tex
Butterworth plots
changes to transfer function flowchart

\begin{figure*}
	\includegraphics[width=.99\textwidth]{figures/pipeline_highlighted.pdf}
	\caption{
Flowchart for the optical microphone transfer function. 
The highlighted stage is analysed in Appendix \jam{XX}, the other stages are left to future work. 
\jam{[to do: change grey to something more readable and reconsider labels. add editable version to git]}
}
	\label{fig:pipeline_highlighted}
\end{figure*}

>>>>

\begin{figure*}
	\includegraphics[height=.99\textwidth, angle=-90]{figures/pipeline.pdf}
	\caption{
Flowchart for the optical microphone transfer function. 
The stage inside the red, dashed box is analysed in Appendix~\ref{app:intensity_derivation}. Understanding the other stages is one part of future work. 
}
	\label{fig:pipeline_highlighted}
\end{figure*}
